Model to study co-evolution of trade an culture

### 2015-03-29 article.tex
done ccl and update discussion

@@

In future works numerous, more realistic and complex dynamics can be studied in the same model. First the constraints on the production could be relaxed so that each agent can choose the products it wishes to produce at the current time step. Moreover meterological factors can modify the quality of the production (noisy outcome of the proces) thus making the process more realistic and more complex~\cite{bentley_specialisation_2005}.

@@

%ACE and prospective trading
More complex models can also be envisionned such as those developed by 
\cite{rubinstein_equilibrium_1985} and to test more general proposal, as those done by \cite{polanyi_trade_1957,polanyi_livelihood_1977} about the early economical mechanisms. Moreover, and in order to be more realistic, and consistently with the cognitive and agent based approach of the project, we will also test assumptions made by people from \emph{Prospect Theory} as proposed by 
\cite{kahneman_prospect_1979}, see also
\cite{camerer_prospect_2004}. The idea here is that traditional economical studies use formal mathematical models that suppose people acting as rational agent, which is a presumption that is far from being valid  in every day life.

Top palliate this problem, Prospect Theory put the focus on the study of the human cognitive abilities and the impact those abilities brings on economics issues. Among various aspect on which prospect theory shed light one can look at how cognitive abilities modify the decisions-making process of human under risk
\cite{weber_disposition_1998}.

Moreover, we think that this approach fit perfectly with our agent based modeling approach (also called Agent based Computational Economy, ACE, when dealing with economical problems, see
\cite{tesfatsion_introduction_2001}).

This subjective value is the value that agents ``put'' on each resources. It could be learn using any mechanism of ``social learning'' (as defined by \cite{lycett_cultural_2015}) known in the literature (teaching, different kind of copying mechanisms,\ldots) and/or integrate any cognitive/environmental bias that could be studied (see again \cite{lycett_cultural_2015} for some kind of bias that could be implemented).

In order to test these hypohtesis more advanced agents are naturally envisionned. One possible tracks of investigation is agents endowed with self-adaptation abilities as proposed in Reinforcement Learning or Developmental Learning. Another possibility is to follow the cognitive approaches that propose to model the complexity of the human behaviour in general representations such as BDI and XXXX.

>>>>

This article has propose a framework to study both cultural transmission mechanisms and trade mechanisms. Our framework is based on a central element, the value vector, which is interpreted differently depending on the mechanisms studied. We have shown the validity of this approach by reproducing expected results on both the cultural and trade side. On the cultural transmission side we have shown that the implementation of the ``neutral model" leads to the expected observations on the variants of the vector value: a power law. When implementing trading mechanisms we observe the convergence of prices to the expected values and the improvement of the scores of the agents.

On top of these results, by the implementation of trade mechanisms as cultural mechanisms, we show that trade is plainly a cultural factor. The modifications needed in our framework where relative to the proposition of new imitation and innovation mechanisms which are typical of the study of the cultural transmission. This proximity between trade mechanisms and cultural transmission allows for the comparisons of the results obtained. For example, it has been possible here to compare the distribution of values obtained and highlight that the divergence from a power law actually is coming mainly from the imitation mechanism used in trade. Moreover this imitation mechanism can further be interpreted as a ``prestige bias" imitation already studied in cultural transmission.

@@

In future works numerous, more realistic and complex dynamics can be studied in the same model. First the constraints on the production could be relaxed so that each agent can choose the products it wishes to produce at the current time step. Moreover, meterological factors can modify the quality of the production (noisy outcome of the process) thus making the process more realistic and more complex~\cite{bentley_specialisation_2005}.

@@

The trading theories studied also can be extended to the \emph{Prospect Theory}~\cite{kahneman_prospect_1979} which proposes to study more realistic trade mechanisms taking into account the biases of humans. Another economical framework we envision is the Agent based Computational Economy, ACE, which is  addressing economical problems raising from the interactions of a large number of agents~\cite{tesfatsion_introduction_2001}. On top of these trading theories the influence of the network of trades by itself can be studied. Various networks can be envisioned ranging from fully connected to small world, and taking into account possible delays or the sudden rupture of a link.

On the cultural transmission side, the vector value could be learned using any mechanism of ``social learning'' (as defined by \cite{lycett_cultural_2015}) known in the literature (teaching, different kind of copying mechanisms,\ldots) and/or integrate any cognitive/environmental bias that could be studied (see again \cite{lycett_cultural_2015} for some kind of bias that could be implemented). Agents could be also endowed with self-adaptation abilities implemented thanks to Reinforcement Learning or Developmental Learning. Another possible track to implement the self-adaptation abilities is to rely on the cognitive approaches that propose to model the complexity of the human behaviour in general representations such as BDI.
